Smart Model Elimination for Efficient Automated Machine Learning

### 2024-06-22 paper/paper.tex
add spaces
Update paper.tex

\section{Experiments}
\subsection{Experiment Design}
To evaluate our framework, we choose 5 different datasets of diverse size. We ran SMEML on each dataset for 20 iterations of tuning. We compared this against a "dumb" mode which simply runs every model on the dataset. We used the accuracy and time to train as our metrics. All experiments are run on an Ubuntu server with Intel Xeon E5520 @ 2.27GHz and 24GB of RAM.

@@

[1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, journal-article, 16 Apr. 2021, arxiv.org/pdf/1908.00709.
[2] Nchasi, Goodluck, et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports, vol. 5, no. 6, Oct. 2022, doi:10.1002/hsr2.893.
[3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 2016, iris.who.int/bitstream/handle/10665/250368/9789241511131-eng.pdf?sequence=1.
[4] Bajwa, Junaid, et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal, vol. 8, no. 2, July 2021, pp. e188–94, doi:10.7861/fhj.2021-0095.
[5] LeDell, E., and S. Poirier. “H2O AutoML: Scalable Automatic Machine Learning.” 7th ICML Workshop on Automated Machine Learning, 2020, \url{www.automl.org/wp-content/uploads/2020/07/AutoML_2020_paper_61.pdf}.
[6] “H2oai/H2o-3: H2O Is an Open Source, Distributed, Fast and Scalable Machine Learning Platform: Deep Learning, Gradient Boosting (GBM) \& XGBoost, Random Forest, Generalized Linear Modeling (GLM With Elastic Net), K-Means, PCA, Generalized Additive Models (GAM), RuleFit, Support Vector Machine (SVM), Stacked Ensembles, Automatic Machine Learning (AutoML), Etc.” GitHub, github.com/h2oai/h2o-3.
[7] Olson, Randal S., 1, et al. Automating Biomedical Data Science Through Tree-based Pipeline Optimization. journal-article, 28 Jan. 2016, arxiv.org/pdf/1601.07925.
[8] “EpistasisLab/Tpot: A Python Automated Machine Learning Tool That Optimizes Machine Learning Pipelines Using Genetic Programming.” GitHub, github.com/EpistasisLab/tpot.
[9] “Mljar/Mljar-supervised: Python Package for AutoML on Tabular Data With Feature Engineering, Hyper-Parameters Tuning, Explanations and Automatic Documentation.” GitHub, github.com/mljar/mljar-supervised.
[10] Conrad, Felix, et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports, vol. 12, no. 1, Nov. 2022, doi:10.1038/s41598-022-23327-1.
[11] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." arXiv, 11 Nov. 2019, arxiv.org/pdf/1911.04706.
[12] "FLAML: A Fast Library for AutoML and Tuning." GitHub, github.com/microsoft/FLAML.
[13] “Sb-ai-lab/LightAutoML: Fast and Customizable Framework for Automatic ML Model Creation (AutoML).” GitHub, github.com/sb-ai-lab/LightAutoML.
[14] Akalin, Altuna. 3.3 Relationship Between Variables: Linear Models and Correlation | Computational Genomics With R. 30 Sept. 2020, compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html.
\end{document}

>>>>

\section{Experiments}
\subsection{Experiment Design}
To evaluate our framework, we choose 5 different datasets of diverse size [/15, /16, /17, /18, /19, /20]. We ran SMEML on each dataset for 20 iterations of tuning. We compared this against a "dumb" mode which simply runs every model on the dataset. We used the accuracy and time to train as our metrics. All experiments are run on an Ubuntu server with Intel Xeon E5520 @ 2.27GHz and 24GB of RAM.

@@

[1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, journal-article, 16 Apr. 2021, arxiv.org/pdf/1908.00709.

[2] Nchasi, Goodluck, et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports, vol. 5, no. 6, Oct. 2022, doi:10.1002/hsr2.893.

[3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 2016, iris.who.int/bitstream/handle/10665/250368/9789241511131-eng.pdf?sequence=1.

[4] Bajwa, Junaid, et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal, vol. 8, no. 2, July 2021, pp. e188–94, doi:10.7861/fhj.2021-0095.

[5] LeDell, E., and S. Poirier. “H2O AutoML: Scalable Automatic Machine Learning.” 7th ICML Workshop on Automated Machine Learning, 2020, \url{www.automl.org/wp-content/uploads/2020/07/AutoML_2020_paper_61.pdf}.

[6] “H2oai/H2o-3: H2O Is an Open Source, Distributed, Fast and Scalable Machine Learning Platform: Deep Learning, Gradient Boosting (GBM) \& XGBoost, Random Forest, Generalized Linear Modeling (GLM With Elastic Net), K-Means, PCA, Generalized Additive Models (GAM), RuleFit, Support Vector Machine (SVM), Stacked Ensembles, Automatic Machine Learning (AutoML), Etc.” GitHub, github.com/h2oai/h2o-3.

[7] Olson, Randal S., 1, et al. Automating Biomedical Data Science Through Tree-based Pipeline Optimization. journal-article, 28 Jan. 2016, arxiv.org/pdf/1601.07925.

[8] “EpistasisLab/Tpot: A Python Automated Machine Learning Tool That Optimizes Machine Learning Pipelines Using Genetic Programming.” GitHub, github.com/EpistasisLab/tpot.

[9] “Mljar/Mljar-supervised: Python Package for AutoML on Tabular Data With Feature Engineering, Hyper-Parameters Tuning, Explanations and Automatic Documentation.” GitHub, github.com/mljar/mljar-supervised.

[10] Conrad, Felix, et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports, vol. 12, no. 1, Nov. 2022, doi:10.1038/s41598-022-23327-1.

[11] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." arXiv, 11 Nov. 2019, arxiv.org/pdf/1911.04706.

[12] "FLAML: A Fast Library for AutoML and Tuning." GitHub, github.com/microsoft/FLAML.

[13] “Sb-ai-lab/LightAutoML: Fast and Customizable Framework for Automatic ML Model Creation (AutoML).” GitHub, github.com/sb-ai-lab/LightAutoML.

[14] Akalin, Altuna. 3.3 Relationship Between Variables: Linear Models and Correlation | Computational Genomics With R. 30 Sept. 2020, compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html.

[15] Lung Cancer. 15 July 2022, www.kaggle.com/datasets/nancyalaswad90/lung-cancer.

[16] Chronic KIdney Disease Dataset. 13 Apr. 2017, www.kaggle.com/datasets/mansoordaku/ckdisease.

[17] Busekseolu. Diabetes Classification. 26 Nov. 2021, www.kaggle.com/code/busekseolu/diabetes-classification/input.

[18] Mahendrasinghrajpoot. Brain Stroke Dataset. 21 Aug. 2022, www.kaggle.com/code/mahendrasinghrajpoot/brain-stroke-dataset/input.

[19] Thomaskonstantin. Analyzing and Modeling Stroke Data. 6 July 2021, www.kaggle.com/code/thomaskonstantin/analyzing-and-modeling-stroke-data/input.

[20] Robikscube. Eye State Prediction Dataset. 26 June 2022, www.kaggle.com/code/robikscube/eye-state-prediction-dataset/input?select=EEG_Eye_State_Classification.csv.

\end{document}
